---
title: "Reproducible Research Project Assigment 2"
author: "antitov"
date: "5-April-2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, cache=FALSE,  warning=FALSE, results="show")
options(scipen = 1, digits = 3)
```

#1. Overview aka Synopsis
This report will cover the analysis of Storm Data report prepared by NATIONAL WEATHER SERVICE.

### Underlying goal of analysis
The analysis was drive to answer two following questions:
1. Across the United States, which types of events are most harmful with respect to population health?
2. Across the United States, which types of events have the greatest economic consequences?

#2. Data Processing

```{r, cache = TRUE}
library(data.table)
library(ggplot2)
library(plyr)

fileURL <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2FStormData.csv.bz2"
download.file(fileURL,"stormdata.csv.bz2")
stormdata <- read.table("stormdata.csv.bz2", fill = TRUE, sep = ",",  nrows = 3500, header = TRUE)

```


#2. Teh report

Let us analyse injuries and fatalities of StormData Report.

Here is numerical analysis of positive injurie cases:
```{r}
summary(stormdata$INJURIES[stormdata$INJURIES>0])
```
Here is numerical analysis of positive fatalities cases:
```{r}
summary(stormdata$FATALITIES[stormdata$FATALITIES>0])

```
Let us define parameters for harmful storm  with respect to population health:

* Number of fatalities is more than 0
* Nmber of injuries is more than median of nonzero injury event distribution, which is `r median(stormdata$INJURIES[stormdata$INJURIES>0])`
```{r}
unique(stormdata[stormdata$FATALITIES>0 | stormdata$INJURIES>5,]$EVTYPE)
```

Here is dependency of Fatalities on Injuries.
```{r}
g = ggplot(stormdata, aes(INJURIES, FATALITIES))
g = g +geom_point() + geom_smooth(method='lm',formula = y ~ poly(x, 2))
print(g)
```
```{r, echo= FALSE}
dev.off()
```
Lets analyze cumulative number of injuries and fatalities by event type.
```{r}
summary_inj_fat <- aggregate(cbind(INJURIES,FATALITIES) ~ EVTYPE, stormdata[stormdata$FATALITIES>0 | stormdata$INJURIES>5,], sum)
g = ggplot(data = as.data.frame(summary_inj_fat), aes(x = EVTYPE, y = INJURIES, fill = INJURIES))
g = g +geom_bar(stat="identity") + scale_fill_gradient2(low='red', mid='yellow', high='darkgreen', space='Lab')

print(g)
```
```{r, echo= FALSE}
dev.off()
```
```{r}
summary(stormdata$PROPDMG)
summary(stormdata$PROPDMG[stormdata$PROPDMG>0])
```
https://rpubs.com/Ziere/RepData_PeerAssessment2

